HW! - Regression Model - 621

### 2020-09-10 HW1/reg_model_shamp.Rmd
updated modeling

```{r, message=FALSE}
train_df <- complete(mice(data = train_df, 
                         method = "norm", 
                         seed = 9450, 
                         print=FALSE), 3)
```

@@

Triples and singles seem to be candidates to remove from the analysis.

```{r}
lm_1<- lm(TARGET_WINS ~ TEAM_BATTING_2B +TEAM_BATTING_HR+
          TEAM_BATTING_BB+TEAM_BATTING_SO+ TEAM_BASERUN_SB+TEAM_BASERUN_CS+
          TEAM_PITCHING_HR+ TEAM_PITCHING_BB+TEAM_PITCHING_SO+TEAM_PITCHING_H+
          TEAM_FIELDING_E+ TEAM_FIELDING_DP+OBP+ SLG, data=train_df)
summary(lm_1)
```

@@

test_df <- complete(mice(data = test_df,
                         method = "norm",
                         seed = 9450,
                         print=FALSE), 3)

@@

Wow. max of 944, not good. How many terrible predictions are there? Let's filter by predictions beyond the currentl MLB season wins record of 116.

```{r}
test_pred %>%
  filter(predictions >= 116)
```

Ten beyond the record, two of which are somewhat reasonable. The rest are not reasonable.

>>>>

```{r, message=FALSE}
train_df <- complete(mice(data = train_df, 
                         method = "pmm", 
                         seed = 9450, 
                         print=FALSE), 3)
```

@@

Triples, singles, and pitching hits seem to be candidates to remove from the analysis.

```{r}
lm_1<- lm(TARGET_WINS ~ TEAM_BATTING_2B +TEAM_BATTING_HR+
          TEAM_BATTING_BB+TEAM_BATTING_SO+ TEAM_BASERUN_SB+TEAM_BASERUN_CS+
          TEAM_PITCHING_HR+ TEAM_PITCHING_BB+TEAM_PITCHING_H+
          TEAM_FIELDING_E+ TEAM_FIELDING_DP+OBP+ SLG, data=train_df)
summary(lm_1)
```

## Remove Outliers that Influence Fit

We need further outlier treatment. We will use Cook's distance to remove outliers that are influencing the fit of the model above.

```{r}
cooks_dis<- cooks.distance(lm_1)
influential<- as.numeric(names(cooks_dis)[(cooks_dis > (4/nrow(train_df)))])
train_df<- train_df[-influential, ]
```

@@

test_df <- complete(mice(data = test_df,
                         method = "pmm",
                         seed = 9450,
                         print=FALSE), 3)

@@

Wow. max of 1231, not good. How many terrible predictions are there? Let's filter by predictions beyond the currentl MLB season wins record of 116.

```{r}
test_pred %>%
  filter(predictions >= 116) %>%
  arrange(predictions)
```

Nine beyond the record, three of which are somewhat reasonable. The rest are not reasonable.
